Efficient N-Dimensional surface estimation using Crofton formula and run-length encoding

### 2012-01-12 article/Article.tex
prcision sur le comptage des intersections
ajout de contenu (maths, methodo, precisions)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  hyperref should be the last package to be loaded.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[dvips,
bookmarks,
bookmarksopen,
backref,
colorlinks,linkcolor={blue},citecolor={blue},urlcolor={blue},
]{hyperref}
% to be able to use options in graphics
\usepackage{graphicx}
% for pseudo code
\usepackage{listings}
% subfigures
\usepackage{subfigure}

@@

% Crofton formula
Perimeter measure of 2D objects, surface area measure of 3D objects 
and more generally $(d-1)$-surface measure of $d$-dimensional objects 
can be expressed in a unified formalism by using the Crofton formula.
This formula consists in integrating the intercept number of the object with
lines of various orientation and positions. Its expression in
the general form is:
\begin{eqnarray}
S^{(d-1)}(X) & = & \frac{d v_d}{\pi}\int_{\mathcal{L}^d}\chi\left(X\cap L\right) dL
\end{eqnarray}
where $X$ is the structure of interest, $v_d$ is the volume of the $d$-dimensional ball,
$\mathcal{L}^d$ is the set of all lines in the $d$-dimensional space. 
The Euler-Poincar\'e characteristic $\chi$ is equal to number of connected components
of the intersection of $X$ with a line $L$.

@@

% discretisation
The Crofton formula can be easily applied to discrete binary images. 
The integral over lines can be decomposed into an integral over a finite set of directions
and an integral over lines parallel to a given direction.

@@

\section{Evaluation method}
\subsection{Shape discretization}
\subsection{Test shapes}
\subsection{Measurments}
\subsection{Timing evaluation}

\section{Accuracy}
\subsection{Position effect}
\subsection{Orientation effect}

@@

>>>>

% to be able to use options in graphics
\usepackage{graphicx}
% for pseudo code
\usepackage{listings}
% subfigures
\usepackage{subfigure}

% some maths symbols
\usepackage{amstext,amssymb}

% to include accents in bliblio
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  hyperref should be the last package to be loaded.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[dvips,
bookmarks,
bookmarksopen,
backref,
colorlinks,linkcolor={blue},citecolor={blue},urlcolor={blue},
]{hyperref}

@@

% Crofton formula
Perimeter measure of 2D objects, surface area measure of 3D objects 
and more generally $(d-1)$-surface measure of $d$-dimensional objects 
can be expressed in a unified formalism by using the Crofton formula.
This formula consists in integrating the intercept number of the object with
lines of various orientation and positions. Its expression in
the general form is:
\begin{eqnarray}
S^{(d-1)}(X) & = & \frac{d v_d}{\pi}\int_{\mathcal{L}^d}\chi\left(X\cap L\right) dL
\end{eqnarray}
where $X$ is the structure of interest, $v_d$ is the volume of the $d$-dimensional ball,
$\mathcal{L}^d$ is the set of all lines in the $d$-dimensional space. 
The above integral is normalised such that the mass of lines hitting the unit ball 
equals $v_{d-1}$, the measure of the unit ball projection on a $(d-1)$-dimensional plane.

The Euler-Poincar\'e characteristic $\chi$ is equal to number of connected components
of the intersection of $X$ with a line $L$, or equivalently half the number of intersections
of the boundary of $X$ with the line.

@@

% discretisation
The Crofton formula can be easily applied to discrete binary images \cite{Lang2001, Legland2007}. 
The integral over lines can be decomposed into an integral over a finite set of directions
and an integral over lines parallel to a given direction.
The number of connected components in the intersections of the structure with a discrete line
is obtained by counting the number of intercepts with its boundary.

@@

The (planar) circularity (often called "shape factor") is defined as:
\begin{eqnarray}
f = 4\pi \frac{A}{p^2}
\end{eqnarray}

Circularity takes values between $0$ and $1$. It is equal to $1$ for circular shapes, and decreases for elongated shapes.

[on garde la circularité ?]

\section{Evaluation method}

\subsection{Test shapes}

Perimeter and surface area are measured on discretization of various 2D and 3D shapes 
whose true perimeter or surface area is known.

Planar test shapes include:
\begin{itemize}
\item disks
\item ring, obtained by the difference of several disks
\item trefoil shape
\item ellipses with $a=XX$ and $b=XX$
\item rectangle with length $XX$ and width $XX$
\end{itemize}

% % Example of reconstruction of a discrete disk
% \begin{figure}[!htb]
% \begin{center}
% \includegraphics[width=5cm]{discreteDisk.eps}
% %\includegraphics[width=5cm][bb=0 0 605 605]{chick.png}
% \end{center}
% \end{figure}

Test shapes for 3D measurements include:
\begin{itemize}
\item balls with various radii
\item hollow ball
\item prolate and oblate ellipsoids
\item cuboids
\end{itemize}

\subsection{Shape discretization}

A 2D or 3D binary image can be considered as a subset of a rectangular grid $L_d$ where
d = 2,3. Such a grid can be written as
\begin{eqnarray}
L_d = \Delta_{1} \mathbb{Z} \times \ldots \times \Delta_{1} \mathbb{Z},
\end{eqnarray}

where the $d$-uple $(\Delta_{1},\ldots,\Delta_{d})$ defines the pixel
or voxel size. A digitization scheme represents how a continuous
structure $X$ is digitized into a binary image $X_\text{d}$. According to
the lattice scheme, $X_\text{d} = X\cap\mathbb{L}^d$. According to the
covering scheme a grid point $x$ belongs to $X_\text{d}$ if the grid
cell centered on $x$ hits $X$. 
This paper assumes isotropic resolution, i.e. $\Delta_{i}$ being the same for all $i$.

\subsection{Measurements}

For each test shape, measurements were made on
several discretisation of the shape, with various orientations and various origins.

The center of each shape was chosen at random within the center pixel or voxel of the grid.

\subsection{Timing evaluation}

???

\section{Accuracy}

\subsection{Global accuracy}

[Tableaux qui donnent les valeurs moyennes pour les differentes formes]

%
\begin{table}[!htb]
\begin{center}
\begin{tabular}{|c|c|c|c|} \hline 
shape		    & $U$		& $U_d^2$ & $U_d^4$		\tabularnewline \hline
disk		    & $251.33$	& $251.31$ 	& $251.32$ 	\tabularnewline
ring		    & $376.99$	& $376.99$ 	& $377.02$	\tabularnewline
rectangle  $0$ 	& $120.00$ 	&\ \ $94.24$& $112.66$	\tabularnewline
rectangle $30$  & $-$ 		& $127.23$	& $120.82$	\tabularnewline
rectangle $45$  & $-$ 		& $131.95$	& $113.18$	\tabularnewline
\hline
\end{tabular}\end{center}
\caption{\label{tab:Validate-Perimeter}
Differences between theoretical and measured perimeter of planar shapes.
Approximations were computed using $2$ and $4$ directions.
}
\end{table}

\subsection{Position effect}

[On regarde effet de la resolution et de la dispersion des mesures]
[-> 1 graphe 2D, 1 graphe 3D, avec superposition des mesures ?]

\subsection{Orientation effect}

@@

[c'est rapide]
